My Linux Notes

### 2018-07-12 Ubuntu_16.04_setup/mylinux.Rmd
up

Findout IP address locally:
```bash
hostname -I | awk '{print $1}'
```

@@

1. Fix floating IP
2. configurate prompt
3. Auto Turn on

>>>>

Findout IP address locally: `hostname -I`

@@

1. Fix floating IP
(Alternative: auto push IP address when turned on
https://superuser.com/questions/471253/ubuntu-how-to-run-a-terminal-command-on-boot)
2. Auto Turn-on Computer at 
	- Enter `BIOS` > `Power Management Setup` > Enable `Power on by RTC Alarm` > Set `Date & Time`[^utc]

[^utc]: Note the date time is in [Coordinated Universal Time (UTC) Standard](https://en.wikipedia.org/wiki/Coordinated_Universal_Time), so it's -8 hrs from the time in Taiwan.
